Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-09-01 paper/SST/SST_main.tex
添加了 SST 和 Q 的修改意见文件；添加了修改计划
添加并测试了修改使用的 changes 宏包；修正了 tex2docx 的部分bug
1. changes 在编译时运行正常，但在使用 pandoc 转 word 时无法正常显示。
2. tex2docx 生成的 docx 显示报错时优先删除流程图部分。

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin}
        \caption{}
        \label{fig:stru-Visairo}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-serial}
        \caption{}
        \label{fig:stru-Visairo-serial}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-parallel}
        \caption{}
        \label{fig:stru-Visairo-parallel}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-isolate}
        \caption{}
        \label{fig:stru-Visairo-isolate}
    \end{subfigure}
    \caption{
        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
        all batteries in (b) series connection, (c) parallel connection, and
        (d) battery $B_3$ isolated.
        }
    \label{fig:arch}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{main}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-he}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-xu}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-my}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{battery_simple}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{stru-L-origin}
        \caption{}
        \label{fig:study-stru-Lawson}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin}
        \caption{}
        \label{fig:study-stru-Visairo}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{stru-my-origin}
        \caption{}
        \label{fig:study-stru-my}
    \end{subfigure}
    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-topo}
        \caption{}
        \label{fig:study-dirgraph-my}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp1}
        \caption{}
        \label{fig:sp1}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp2}
        \caption{}
        \label{fig:sp2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp3}
        \caption{}
        \label{fig:sp3}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp4}
        \caption{}
        \label{fig:sp4}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-mac}
        \caption{}
        \label{fig:study-results-my}
    \end{subfigure}
    \caption{
        For the RBS structure in Figure \ref{fig:study-stru-my}, 
        (a)its directed graph 
        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
        (f)The circuit of the RBS with its output reaching the MAC.
        }
    \label{fig:all-results-my}
\end{figure}

@@

\begin{table}[htbp]
    \centering
    \caption{
      The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al. , and the structure proposed in this paper.
      }
      \label{tab:isolated_mac}
      \begin{tabular}{cccc}
      \toprule
      \multirow{2}[4]{*}{number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
  \cmidrule{2-4}          & our  & Visairo's  & Lawson's  \\
      \midrule
      0     & 2     & 4     & 1 \\
      1     & 2     & 3     & 1 \\
      2     & 2$^{\rm a}$ or 1$^{\rm b}$ & 2     & 1 \\
      3     & 1     & 1     & 1 \\
      \bottomrule
      \end{tabular}
      \\
      \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
      \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
  \end{table}

  \begin{figure}[htbp]
      \centering
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-1}
          \caption{}
          \label{fig:my-isolated-1}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-2b}
          \caption{}
          \label{fig:my-isolated-2b}
      \end{subfigure}
      \\
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-2w}
          \caption{}
          \label{fig:my-isolated-2w}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-3}
          \caption{}
          \label{fig:my-isolated-3}
      \end{subfigure}
      \caption{
          The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Figure \ref{fig:study-stru-my}.
          }
  \end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers

@@

\usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b} 原文的b替换成a
% \usepackage[final]{changes}

% 按 Q 修改意见修改 0901 【优先】
% 按 SST 修改意见修改 0902 【14号前交给润色机构】
% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
% 2. 介绍修改，相关文献：
%   2.1 RBS 结构分析相关的
%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin.png}
        \caption{}
        \label{fig:stru-Visairo}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-serial.png}
        \caption{}
        \label{fig:stru-Visairo-serial}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-parallel.png}
        \caption{}
        \label{fig:stru-Visairo-parallel}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-isolate.png}
        \caption{}
        \label{fig:stru-Visairo-isolate}
    \end{subfigure}
    \caption{
        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
        all batteries in (b) series connection, (c) parallel connection, and
        (d) battery $B_3$ isolated.
        }
    \label{fig:arch}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{main.png}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-he.png}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-xu.png}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-my.png}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{stru-L-origin.png}
        \caption{}
        \label{fig:study-stru-Lawson}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin.png}
        \caption{}
        \label{fig:study-stru-Visairo}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{stru-my-origin.png}
        \caption{}
        \label{fig:study-stru-my}
    \end{subfigure}
    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-topo.png}
        \caption{}
        \label{fig:study-dirgraph-my}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp1.png}
        \caption{}
        \label{fig:sp1}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp2.png}
        \caption{}
        \label{fig:sp2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp3.png}
        \caption{}
        \label{fig:sp3}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp4.png}
        \caption{}
        \label{fig:sp4}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-mac.png}
        \caption{}
        \label{fig:study-results-my}
    \end{subfigure}
    \caption{
        For the RBS structure in Figure \ref{fig:study-stru-my}, 
        (a)its directed graph 
        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
        (f)The circuit of the RBS with its output reaching the MAC.
        }
    \label{fig:all-results-my}
\end{figure}

@@

\begin{table}[htbp]
    \centering
    \caption{
      The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al. , and the structure proposed in this paper.
      }
      \label{tab:isolated_mac}
      \begin{tabular}{cccc}
      \toprule
      \multirow{2}[4]{*}{number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
  \cmidrule{2-4}          & our  & Visairo's  & Lawson's  \\
      \midrule
      0     & 2     & 4     & 1 \\
      1     & 2     & 3     & 1 \\
      2     & 2$^{\mathrm{a}}$ or 1$^{\mathrm{b}}$ & 2     & 1 \\
      3     & 1     & 1     & 1 \\
      \bottomrule
      \end{tabular}
      \\
      \footnotesize{$^{\mathrm{a}}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
      \footnotesize{$^{\mathrm{b}}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
  \end{table}

  \begin{figure}[htbp]
      \centering
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-1.png}
          \caption{}
          \label{fig:my-isolated-1}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-2b.png}
          \caption{}
          \label{fig:my-isolated-2b}
      \end{subfigure}
      \\
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-2w.png}
          \caption{}
          \label{fig:my-isolated-2w}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{my-isolated-3.png}
          \caption{}
          \label{fig:my-isolated-3}
      \end{subfigure}
      \caption{
          The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Figure \ref{fig:study-stru-my}.
          }
  \end{figure}
